Subjective Experience of Demands and Resources across O*NET Job Elements

### 2024-02-24 Submission.Rmd
desktop edits
small edits
coffee shop edits - shift focus to CH (from JDR)

@@

@@

Appraisals are associated with different forms of coping, and subsequently, outcomes. The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing. A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic. @kim2020thriving found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing. The opposite occurred when a demand was appraised as a hindrance – in those instances, the appraisal had a negative association with motivational resources. @cavanaugh2000empirical, in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern. @chen2021daily found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment. Daily hindrance demands were negatively related to these outcomes. In contrast, @abbas2019challenge found that challenge and hindrance stressors were *both* positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it [@crawford2010linking]. Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety [@rodell2009can]. Lastly, @gerich2017relevance concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.

@@

The integration of the literature above culminates with two primary hypotheses. The first addresses whether employees generally agree on their appraisals of job characteristics as resources or challenge or hindrance demands. For instance, although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, others have reported variability in these appraisals [e.g., @lepine2022challenge]. @lepine2022challenge, in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal. Thus, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance. COMBINE 1 and 2:

>Hyp 3: Are these perceptions aligned with the literature's presentation of job characteristics?

The second set of analyses focuses on associations. Do demands and resources have implications for work outcomes?

>Hyp 4.a: Job resources are associated with greater engagement, less stress, and less burnout. 
>Hyp 4.b: More hindrances leads to less engagement, more stress, and greater burnout.

>Hyp 4.exploratory: More challenges leads to greater satisfaction, engagement, and burnout.

@@

>>>>

Outline:
Work toward model (picture)

+ Challenge-hindrance framework
  + Cavanaugh (~2000)
  + Last 20 years' research (variance - look at Pindek et al, 2024)
  + Appraisals

+ Antecedents (job elements)
  a. O\*Net - comprehensive
III. Consequences (outcomes)
  a. Moderation
IV. Contribution
  a. include resources

@@

## ARGUE FOR H1 and H2 (Are perceptions universal?)

Add resources here

@@

## Connecting appraisals to workplace outcomes[^thought]

[^thought]: add a sentence that adds a brief description of working conditions to first paragraph. Whole section needs expansion.

The second set of analyses focuses on associations. Do demands and resources have implications for work outcomes? Appraisals are associated with different forms of coping, and subsequently, outcomes. See Figure 1 for proposed associations. The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing. A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic. @kim2020thriving found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing. The opposite occurred when a demand was appraised as a hindrance – in those instances, the appraisal had a negative association with motivational resources. @cavanaugh2000empirical, in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern. @chen2021daily found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment. Daily hindrance demands were negatively related to these outcomes. In contrast, @abbas2019challenge found that challenge and hindrance stressors were *both* positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it [@crawford2010linking]. Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety [@rodell2009can]. Lastly, @gerich2017relevance concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.

@@

The integration of the literature above culminates with two primary hypotheses. The first addresses whether employees generally agree on their appraisals of job characteristics as resources or challenge or hindrance demands. For instance, although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, others have reported variability in these appraisals [e.g., @lepine2022challenge]. @lepine2022challenge, in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal. Thus, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.

```{r ourmodel, eval=TRUE, echo=FALSE, fig.cap="This is our working model"}
library(magick)
library(grid)

figure2 <- image_read("ourmodel.png")

grid.raster(figure2) # works well with margins/etc

Our model is represented in Figure \@ref(fig:ourmodel)

>Hyp 3.a: Job resources are associated with greater engagement, less stress, and less burnout.

>Hyp 3.b: More hindrances leads to less engagement, more stress, and greater burnout.

>Hyp 3.exploratory: More challenges leads to greater satisfaction, engagement, and burnout.[^figure]

[^figure]: These need to be reframed to match Figure 1.

@@

Cross-sectional

### 2024-02-24 Submission.tex
small edits
coffee shop edits - shift focus to CH (from JDR)

@@

@@

Appraisals are associated with different forms of coping, and subsequently, outcomes. The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing. A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic. Kim and Beehr (2020) found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing. The opposite occurred when a demand was appraised as a hindrance -- in those instances, the appraisal had a negative association with motivational resources. Cavanaugh et al. (2000), in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern. Chen et al. (2021) found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment. Daily hindrance demands were negatively related to these outcomes. In contrast, Abbas and Raja (2019) found that challenge and hindrance stressors were \emph{both} positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it (Crawford et al., 2010). Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety (Rodell \& Judge, 2009). Lastly, Gerich (2017) concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.

@@

The integration of the literature above culminates with two primary hypotheses. The first addresses whether employees generally agree on their appraisals of job characteristics as resources or challenge or hindrance demands. For instance, although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, others have reported variability in these appraisals (e.g., M. A. LePine, 2022). M. A. LePine (2022), in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal. Thus, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance. COMBINE 1 and 2:

\begin{quote}
Hyp 3: Are these perceptions aligned with the literature's presentation of job characteristics?
\end{quote}

The second set of analyses focuses on associations. Do demands and resources have implications for work outcomes?

\begin{quote}
Hyp 4.a: Job resources are associated with greater engagement, less stress, and less burnout.
Hyp 4.b: More hindrances leads to less engagement, more stress, and greater burnout.
\end{quote}

\begin{quote}
Hyp 4.exploratory: More challenges leads to greater satisfaction, engagement, and burnout.
\end{quote}

>>>>

Outline:
Work toward model (picture)

\begin{itemize}
\tightlist
\item
  Challenge-hindrance framework

  \begin{itemize}
  \tightlist
  \item
    Cavanaugh (\textasciitilde2000)
  \item
    Last 20 years' research (variance - look at Pindek et al, 2024)
  \item
    Appraisals
  \end{itemize}
\item
  Antecedents (job elements)

  \begin{enumerate}
  \def\labelenumi{\alph{enumi}.}
  \tightlist
  \item
    O*Net - comprehensive
  \end{enumerate}
\end{itemize}

\begin{enumerate}
\def\labelenumi{\Roman{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  Consequences (outcomes)
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\tightlist
\item
  Moderation
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\Roman{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  Contribution
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\tightlist
\item
  include resources
\end{enumerate}

@@

\hypertarget{argue-for-h1-and-h2-are-perceptions-universal}{%
\subsection{ARGUE FOR H1 and H2 (Are perceptions universal?)}\label{argue-for-h1-and-h2-are-perceptions-universal}}

Add resources here

@@

\hypertarget{connecting-appraisals-to-workplace-outcomesthought}{%
\subsection[Connecting appraisals to workplace outcomes]{\texorpdfstring{Connecting appraisals to workplace outcomes\footnote{add a sentence that adds a brief description of working conditions to first paragraph. Whole section needs expansion.}}{Connecting appraisals to workplace outcomes}}\label{connecting-appraisals-to-workplace-outcomesthought}}

The second set of analyses focuses on associations. Do demands and resources have implications for work outcomes? Appraisals are associated with different forms of coping, and subsequently, outcomes. See Figure 1 for proposed associations. The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing. A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic. Kim and Beehr (2020) found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing. The opposite occurred when a demand was appraised as a hindrance -- in those instances, the appraisal had a negative association with motivational resources. Cavanaugh et al. (2000), in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern. Chen et al. (2021) found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment. Daily hindrance demands were negatively related to these outcomes. In contrast, Abbas and Raja (2019) found that challenge and hindrance stressors were \emph{both} positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it (Crawford et al., 2010). Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety (Rodell \& Judge, 2009). Lastly, Gerich (2017) concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.

@@

The integration of the literature above culminates with two primary hypotheses. The first addresses whether employees generally agree on their appraisals of job characteristics as resources or challenge or hindrance demands. For instance, although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, others have reported variability in these appraisals (e.g., M. A. LePine, 2022). M. A. LePine (2022), in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal. Thus, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/ourmodel-1.pdf}
\caption{\label{fig:ourmodel}This is our working model}
\end{figure}

Our model is represented in Figure \ref{fig:ourmodel}

\begin{quote}
Hyp 3.a: Job resources are associated with greater engagement, less stress, and less burnout.
\end{quote}

\begin{quote}
Hyp 3.b: More hindrances leads to less engagement, more stress, and greater burnout.
\end{quote}

\begin{quote}
Hyp 3.exploratory: More challenges leads to greater satisfaction, engagement, and burnout.\footnote{These need to be reframed to match Figure 1.}
\end{quote}
